Extracting data for time slice analyses

### 2017-11-27 analyses/01-extract-data-for-analyses.Rmd
Remove non needed data etc.

The analyses require a NEXUS matrix of characters, a csv file of first and last occurrence dates (FADLAD) and a phylogeny.

@@

## Adding a root age (max tree age date)
tree$root.time <- max(tree.age(tree)[, 1])
```

@@

## Removed taxa, i.e. those in the tree but not the matrix and vice versa
as.vector(na.omit(c(cleaned_data$dropped_tips, cleaned_data$dropped_rows)))
```

@@

Ordinating the matrix
----------------

Ordination is a classic NMDS (multidimensional scaling) including only the non-zero variance axes.

```{r}
## Loading the distance matrices
load(paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix
morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
```

And that's it... we now have all the arguments for running the `dispRity` package properly: the space (`morphospace`), the tree (`tree`) and the FADLAD (`FADLAD`). Remember that for the `time.subsamples` function, you can use the `inc.nodes` logical option to include nodes or not!

@@

@@

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))

>>>>

The analyses require a NEXUS matrix of characters, a csv file of first and last occurrence dates (FADLAD) and a phylogeny. The matrix and phylogeny need to be cleaned and manipulated - we do this below. The FADLAD can be read in as is so doesn't get read in until we need it for analyses in later scripts.

@@

## Adding a root age (max tree age date)
## Note that we need to redo this in the `02-time-slice-analyses` scripts
## as write.nexus/tree won't save root times
tree$root.time <- max(tree.age(tree)[, 1])
```

@@

## Removed taxa, i.e. those in the tree but not the matrix and vice versa
as.vector(na.omit(c(cleaned_data$dropped_tips, cleaned_data$dropped_rows)))

## Saving the tree
write.nexus(tree, file = paste0("../data/processed/tree.", slug ,".tre"))
```

@@

And that's it... we now have all the processed data for running the `dispRity` package properly: the distance matrices(that we will use to build the `morphospace`), and the cleaned tree (`tree`). Remember that for the `time.subsamples` function, you can use the `inc.nodes` logical option to include nodes or not!

@@

## Removed taxa, i.e. those in the tree but not the matrix and vice versa
as.vector(na.omit(c(cleaned_data$dropped_tips, cleaned_data$dropped_rows)))

## Saving the tree
write.nexus(tree, file = paste0("../data/processed/tree.", slug ,".tre"))

@@

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))
```
